### 2017-06-15 paper.tex
removing extra " from #4

Thinking systematically about difficulty levels can help manage expectations.
For example,
Programming Historian project labels lessons ``beginner''",
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
This method works, however, only if there is prior agreement on what those terms mean.

>>>>

Thinking systematically about difficulty levels can help manage expectations.
For example,
Programming Historian project labels lessons ``beginner'',
``intermediate'',
and ``advanced''
to help authors write at appropriate levels.
This method works, however, only if there is prior agreement on what those terms mean.
